NURM: a tool to locate numerical differences in pipelines

### 2019-05-28 paper.tex
More edits and comments

  \State /* Input: - a list of n trees; \texttt{T = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State /*\quad \quad \quad \quad - a distance threshold value; \texttt{threshold}
  \State /* Output: a list of clusters; \texttt{C = [c${_1}$,c${_2}$,...,c${_k}$]}
  \State \texttt{\# Create a cluster for each tree in input list;}
  \State \texttt{C = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State \texttt{\# Define a 2 $\times$ 2 array to store distances}
  \State \texttt{D} = \texttt{array(n, n)}
  \While{\texttt{len(C)} > \texttt{1}}  
  \State \texttt{\# Select the two nearest clusters}
  \For{\texttt{i=1} to \texttt{n}}
  \For{\texttt{j=i+1} to \texttt{len(C)}}
  \State \texttt{D[i][j]} = \texttt{edit\_distance(C[i], C[j])} \tristan{how do you define the distance between two clusters?}
    \EndFor
  \EndFor
  \State \texttt{i, j} = $\argmin \left\{ \texttt{D[i][j]}, \ \texttt{i, j} \in \llbracket 1, \texttt{len(C)}\rrbracket^2 \right\}$
  \If{\texttt{D[i][j]} > \texttt{threshold}}
  \State \Return \texttt{C}
  \Else
  \State \texttt{\# Merge C[j] into C[i]}
  \State \texttt{C[i]} = \texttt{merge}(\texttt{C[i] and C[j]})
  \State \texttt{\# Remove C[j] from C}
  \State \texttt{remove(C[j], C)}
  \EndIf
  \EndWhile
%  \State Function edit\_distance (C${_1}$, C${_2}$)
%  \State EndFunction
\end{algorithmic}
\end{algorithm}

@@

Figure~\ref{fig:iterations} illustrates our incremental labelling 
process for the example in Figure~\ref{fig:simple_script}. At every 
step, processes that created differences are shown in red, processes that 
removed differences are in blue, processes that propagated differences are in 
yellow, and other processes (transparent processes) are in green. As in 
Figure~\ref{fig:simple_script}, plain black edges represent the process 
tree and dashed edges represent file dependencies: green edges 
represent files with no differences, while red edges represent files with 
differences. Temporary files are not represented because they have been 
backed up as previously described.

@@

@@

The Human Connectome Project (HCP)~\cite{glasser2013minimal} developed 
a set of pipelines to help extraction of structural, functional or 
diffusion MRI data across a large set of high resolution MR images. 
These pre-processing pipelines create results that are available in 
standard volume and combined surface and volume spaces which makes it 
easier for researchers to compare the images across the neuroimaging 
spectrum.

We focused on HCP structural pre-processing pipelines to (1)quantify 
the effect of OS on HCP pre-processing pipelines (2) identify the 
process(es) in the pipelines that are responsible for such effects.

The structural pre-processing pipelines consists of PreFreeSurfer, 
FreeSurfer and PostFreeSurfer. In this paper, 
we analyzed PreFreeSurfer pipeline which consist of various steps 
including correction of MR 
gradient nonlinearity distortions, align the T1w and T2w images using 
FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
to T1w using FLIRT's BBR, perform a bias field correction, and register 
the subject's native structural space to MNI space.

>>>>

  \State /* Input: - a list of n trees; \texttt{T = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State /*\quad \quad \quad \quad - a distance threshold value; \texttt{threshold}
  \State /* Output: a list of clusters; \texttt{C = [c${_1}$,c${_2}$,...,c${_k}$]}
  \State \texttt{\# Create a cluster for each tree in input list;}
  \State \texttt{C = [ [t${_1}$], [t${_2}$], \ldots , [t${_n}$] ]}
  \State \texttt{\# Define a 2 $\times$ 2 array to store distances}
  \State \texttt{D} = \texttt{array(n, n)}
  \While{\texttt{len(C)} > \texttt{1}}  
  \State \texttt{\# Select the two nearest clusters}
  \For{\texttt{i=1} to \texttt{n}}
  \For{\texttt{j=i+1} to \texttt{len(C)}}
  \State \texttt{D[i][j]} = \texttt{edit\_distance(C[i], C[j])} \tristan{how do you define the distance between two clusters?}
    \EndFor
  \EndFor
  \State \texttt{i, j} = $\argmin \left\{ \texttt{D[i][j]}, \ \texttt{i, j} \in \llbracket 1, \texttt{len(C)}\rrbracket^2 \right\}$
  \If{\texttt{D[i][j]} > \texttt{threshold}}
  \State \Return \texttt{C}
  \Else
  \State \texttt{\# Merge C[j] into C[i]}
  \State \texttt{C[i]} = \texttt{merge}(\texttt{C[i] and C[j]})
  \State \texttt{\# Remove C[j] from C}
  \State \texttt{remove(C[j], C)}
  \EndIf
  \EndWhile
%  \State Function edit\_distance (C${_1}$, C${_2}$)
%  \State EndFunction
\end{algorithmic}
\end{algorithm}

@@

Figure~\ref{fig:iterations} illustrates our incremental labelling 
process for the example in Figure~\ref{fig:simple_script} \tristan{This is outdated, you should
update the figure and revise the text accordingly.}. At every 
step, processes that created differences are shown in red, processes that 
removed differences are in blue, processes that propagated differences are in 
yellow, and other processes (transparent processes) are in green. As in 
Figure~\ref{fig:simple_script}, plain black edges represent the process 
tree and dashed edges represent file dependencies: green edges 
represent files with no differences, while red edges represent files with 
differences. Temporary files are not represented because they have been 
backed up as previously described.

@@

\tristan{Add section introduction. Talk about OS}

@@

\tristan{Add introduction on HCP project and data}

The Human Connectome Project (\href{https://www.humanconnectome.org}{HCP})
developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, in particular PreFreesurfer
and Freesurfer. A detailed description of the analyses done in the
pipelines is available in~\cite{glasser2013minimal}.
% IF NEEDED, ADD MORE DETAILS ABOUT WHAT THE PIPELINES DO
% The structural pre-processing pipelines consists of PreFreeSurfer, 
% FreeSurfer and PostFreeSurfer. In this paper, 
% we analyzed PreFreeSurfer pipeline which consist of various steps 
% including correction of MR 
% gradient nonlinearity distortions, align the T1w and T2w images using 
% FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
% brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
% to T1w using FLIRT's BBR, perform a bias field correction, and register 
% the subject's native structural space to MNI space.

In these experiments, we first quantify the effect of Linux version on
these pipelines. Then we use our NURM tool to identify the processes in the
pipelines that are responsible for such effects.
